---
title: "RMarkdown_j3456_Keele_Simple_Report_5"
author: "W. Greg Alvord, Ph.D."
date: "November 3, 2014"
output: pdf_document
---

Date:     November 3, 2014

To:       Dr. Brandon Keele

          Dr. Claes Ohlen
          
          Dr. Victor Ayala
          
From:     Dr. Greg Alvord, Director

Subject:  Report 5


# Introduction

We now consider the number of variants observed for each macaque.  For the two Ctrl animals, the observations were 7 & 8.  For the two Expt animals, the observations were 3 & 5.  (Here, we deal only with the observations, not with the theoretical distributions.)

You indcicated that the Scientific Community would be in agreement with the idea that the treatment effect could **not** increase the number of variants in a macaque.  

```{r}
Ctrl <- c(7, 8)
Expt <- c(3, 5)
```

We perform a two-sample, *one-sided* t-test.  Here it is: 

```{r}
t.test(Ctrl, Expt, alternative = 'greater')
```

We have used the default t-test, called Welch's Modified t-test.  It accomodates sames with possibly different variances.  Now, we will assume that the variances are equialent. Here is the code: 

```{r}
t.test(Ctrl, Expt, alternative = 'greater', var.equal = TRUE)
```

